%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1, 21 November 2016) written by
% LianTze Lim (liantze@gmail.com), based on the 
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you want to use \orcid or the
%% academicons icons, add "academicons"
%% to the \documentclass options. 
%% Then compile with XeLaTeX or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% When using the "academicons" option,
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font %% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{textcomp}
% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{2E64FE}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
% \addbibresource{sample.bib}
\begin{document}

\name{divyanshu dubey}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \location{Madhya Pradesh, Gwalior}
  \email{ddubey012@gmail.com}
  \phone{Phone}
  \github{github.com/bleed101}
  \linkedin{linkedin.com/in/d-dubey}
%   \github{} % I'm just making this up though.
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want. Extend the right margin by 8cm (=6.8cm marginparwidth + 1.2cm marginparsep)
\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{HPC Sphere Pvt. Ltd. }{Position-Game Developer(Intern)
}{06-2019 to 07-2019}{New Delhi}
\begin{itemize}
\item  Made flow chart to develop the understanding of the game
and to also track the bugs through these flow diagrams
\item Wrote C-Sharp scripts to determine the mechanics and
gameplay of new software.
\item Troubleshot game programming to ensure no mistakes are
made, this was done on a daily basis.
\item Oversee the testing of the game to determine whether it is
up to standards.
\item  Delivered APKs of the game to the client on a daily basis.
\end{itemize}


% \divider

% \cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employe \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}

\cvsection{Projects}
\cvp{Devolt\hspace{1.4em}}{}{09-2018 to 11-2019}{}
{
 Devolt is a 2-Dimension game that was developed on python3.7. I
used the library named PyCharm which is basically used for
developing games in python. I used some concepts of objectoriented programming like classes and creating corresponding
instances, I used Sqlite3 to handle the database and GUI panel I
used Tkinter. I also used basic physics of class 11th, topic named
equation of motion, Kinematics, and projectiles. This game consists
of player and enemy, you have to kill the enemy before it kills you.
}

\divider
\cvp{CUBA\hspace{1.4em}}{}{12-2018 to 01-2019}{}
{
CUBA was developed on a Unity engine, it is a 3-Dimension game. I
wrote C\# scripts for movements and in-game functioning. I used
OOP\textquotesingle s concepts, used animation for switching between levels, this
game consists of thirteen levels. CUBA was developed for windows
platform, I used third party software to combine the binary files
and .dll files to make executable (.exe) file. The player has to dodge
the obstacles to complete the levels.
}

\divider

\cvp{Techload}{}{08-2019 to 10-2019}{}
{
TechLoad is a blogging website, where one can post their blogs
related to technology. User can also manage their blogs by
registering for the tech blog. We have used HTML, CSS, Javascript
in the frontend, and backend was handled in Django
}
\divider

\begin{adjustwidth}{}{-8cm}
\vspace{15em}
{\faCalendar\hspace{.5em}}{JULY3,2020 }{\hspace{13em}DIVYANSHU DUBEY }{\hspace{12em} {\mailsymbol\hspace{.5em}}ddubey012@gmail.com}
\end{adjustwidth}

\end{document}
